P.berghei pir analysis

### 2021-08-31 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Fixed grouping issue for new top_n_gene fun

  all_genes = tpm_avg %>% 
    top_n(wt = mean_tpm, n = n) %>% 
    dplyr::arrange(stage, desc(mean_tpm)) %>% 
    mutate_if(is.numeric, function(x){round(x, digits = 2)}) %>% 
    mutate(mean_tpm = cell_spec(mean_tpm, "html", 
                                color = ifelse(mean_tpm > threshold, "red", "blue")))
  all_genes$short_descr = allgene.info$handy_descriptions[match(all_genes$Geneid, 
                                                                allgene.info$Geneid)]
  all_genes$description = allgene.info$Description[match(all_genes$Geneid, 
                                                         allgene.info$Geneid)]
  all_genes = all_genes %>% 
    kable(format = 'html', 
          caption = paste0(tpm_avg$experiment[1], ' - Top ', n, ' expressed total genes'), 
          escape = FALSE) %>%
    kable_styling() %>% 
    pack_rows(index = kable_index)

  pir_genes = tpm_avg %>% 
    filter(Geneid %in% pir_id) %>% 
    top_n(wt = mean_tpm, n = n) %>% 
    dplyr::arrange(stage, desc(mean_tpm)) %>% 
    mutate_if(is.numeric, function(x){round(x, digits = 2)}) %>% 
    mutate(mean_tpm = cell_spec(mean_tpm, "html", 
                                color = ifelse(mean_tpm > threshold, "red", "blue"))) %>% 
    mutate(Geneid = as.character(Geneid)) %>% 
    mutate(Description = allgene.info$handy_descriptions[match(Geneid, 
                                                               allgene.info$Geneid)]) %>% 
    mutate(Geneid = ifelse(grepl(Geneid,
                                 pattern = 'PBANKA_0100500'),
                           cell_spec(Geneid, bold = TRUE),
                           Geneid)) %>%
    kable(format = 'html', 
          caption = paste0(tpm_avg$experiment[1], ' - Top ', n, ' expressed pir genes'), 
          escape = FALSE) %>% 
    pack_rows(index = kable_index) %>% 
    kable_styling()

>>>>

  tpm_avg <- tpm_avg %>% 
    ungroup %>% 
    group_by(stage)

  all_genes = tpm_avg %>% 
    slice_max(order_by = mean_tpm, n = n) %>% 
    dplyr::arrange(stage, desc(mean_tpm)) %>% 
    mutate_if(is.numeric, function(x){round(x, digits = 2)}) %>% 
    mutate(mean_tpm = cell_spec(mean_tpm, "html", 
                                color = ifelse(mean_tpm > threshold, "red", "blue")))
  all_genes$short_descr = allgene.info$handy_descriptions[match(all_genes$Geneid, 
                                                                allgene.info$Geneid)]
  all_genes$description = allgene.info$Description[match(all_genes$Geneid, 
                                                         allgene.info$Geneid)]
  all_genes = all_genes %>% 
    kable(format = 'html', 
          caption = paste0(tpm_avg$experiment[1], ' - Top ', n, ' expressed total genes'), 
          escape = FALSE) %>%
    kable_styling() %>% 
    pack_rows(index = kable_index)

  pir_genes = tpm_avg %>% 
    filter(Geneid %in% pir_id) %>% 
    slice_max(order_by = mean_tpm, n = n) %>% 
    dplyr::arrange(stage, desc(mean_tpm)) %>% 
    mutate_if(is.numeric, function(x){round(x, digits = 2)}) %>% 
    mutate(mean_tpm = cell_spec(mean_tpm, "html", 
                                color = ifelse(mean_tpm > threshold, "red", "blue"))) %>% 
    mutate(Geneid = as.character(Geneid)) %>% 
    mutate(Description = allgene.info$handy_descriptions[match(Geneid, 
                                                               allgene.info$Geneid)]) %>% 
    mutate(Geneid = ifelse(grepl(Geneid,
                                 pattern = 'PBANKA_0100500'),
                           cell_spec(Geneid, bold = TRUE),
                           Geneid)) %>%
    kable(format = 'html', 
          caption = paste0(tpm_avg$experiment[1], ' - Top ', n, ' expressed pir genes'), 
          escape = FALSE) %>% 
    pack_rows(index = kable_index) %>% 
    kable_styling()
